Using Cell Phone Keyboards is \NP\ Hard

### 2010-06-30 slides/talk.tex
This is the version that got published.

\fst{So many letters \ldots}{
\begin{itemize}
    \item People want to use phones to send text messages
    \item English has 26 letters, and each letter cas a lower-case and capital form, and we should not forget numbers, puctuation, and whitespace characters.
    \item Other languages have even more!\footnote{Can you name a language with fewer letters than English?\\}
\end{itemize}
}

@@

\section{Summary}
\fst{Future Work}{
\begin{itemize}
    \item Predictive T-9
    \item Other input methods
    \item When T-9 gets a misspelled word, it is very bad and confusing.  Can we minimize not just t9onyms, but also the number of words that have a cell-phone Levenshtein distance of 1? of 2? of $k$?
    \item We completely ignored the pauses that the standard method requires when typing two letter in a row which involve the same key
    \item Completely solving the particular case of T-9 with the English language and an 8-key keyboard
\end{itemize}
}
\fst{Take-away Messages}{
\begin{itemize}
    \item Cell phone keyboards can provide algorithmic fun
    \item The standard input method can be optimized with the greedy algorithm
    \item The T-9 input method is NP-Complete to optimize
    \item The existing keyboard seems alright for T-9, but can be improved by 28\% for the standard input method without breaking legacy advertising
    \item Cell phone keyboards are not just hard to use, they can also be \NP-hard to use
\end{itemize}
}

>>>>

\fst{So many letters \ldots}{
\begin{itemize}
    \item People want to use phones to send text messages
    \item English has 26 letters, and each letter has a lower-case and capital form, and we should not forget numbers, puctuation, and whitespace characters.
    \item Other languages have even more!\footnote{Can you name a language with fewer letters than English?\\}
\end{itemize}
}

@@

\section{Summary}
\fst{Future Work}{
\begin{itemize}
    \item Predictive T-9
    \item Other input methods
    \item When T-9 gets a misspelled word, it is very bad and confusing.  Can we minimize not just t9onyms, but also the number of words that have a cell-phone Levenshtein distance of 1? of 2? of $k$?
    \item We completely ignored the pauses that the standard method requires when typing two letter in a row which involve the same key
    \item Completely solving the particular case of T-9 with the English language and an 8-key keyboard
    \item Universal keyboards --- fixed labelings which are good for multiple languages using the standard typing method (thanks Markus Holzer!)
\end{itemize}
}
\fst{Take-away Messages}{
\begin{itemize}
    \item Cell phone keyboards can provide algorithmic fun
    \item The standard input method can be optimized with the greedy algorithm
    \item The T-9 input method is NP-Complete to optimize
    \item The existing keyboard seems alright for T-9, but can be improved by 28\% for the standard input method without breaking legacy advertising
    \item Cell phone keyboards are not just hard to use, they can also be \NP-hard to use
\end{itemize}
}
